InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Apply suggestions from code review
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline, to stack and apply them together on the content.

The resulting pipelines, especially for the images, were very resource intensive and could not be run efficiently on our own machines. We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that would speed up the pipelines up to 40x compared to our local execution time and allowed to have the same environment for all experiments.

>>>>

For the ease of use and low time consumption we implemented a simple python command line interface, that makes it easy to define a pipeline consisting of a generator, processor and evaluator. It is also possible to enter multiple processors for one pipeline to stack and apply them together on the content.

The resulting pipelines, especially for images, were very resource intensive and could not be run efficiently on our own machines. We chose to use the free Google Colab resources, consisting of a NVIDIA Tesla T4 GPU that speeds up the pipelines up to 40x compared to our local execution time and allowed us to use the same environment for all experiments.
